Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-13 final_metrics_analysis.Rmd

```{python exploratory age by race plot}
# age distribution by race
ax = sns.kdeplot(x="age", hue="race", data=df_viz);
kdeline = ax.lines[0]
mean_fem = df_viz.groupby('race').age.median()[0]
xs = kdeline.get_xdata()
ys = kdeline.get_ydata()
height_fem = np.interp(mean_fem, xs, ys)
ax.vlines(mean_fem, 0, height_fem, color=purple, ls=':')

mean_m = df_viz.groupby('race').age.median()[1]
height_m = np.interp(mean_m, xs, ys)
ax.vlines(mean_m, 0, height_m, color=green, ls=':')

print(df_viz.groupby('race').age.median())

plt.title('Distribution of Age by Race')
```

>>>>

```{python exploratory age by race plot}
# age distribution by race
#ax = sns.kdeplot(x="age", hue="race", data=df_viz);
#kdeline = ax.lines[0]
#mean_fem = df_viz.groupby('race').age.median()[0]
#xs = kdeline.get_xdata()
#ys = kdeline.get_ydata()
#height_fem = np.interp(mean_fem, xs, ys)
#ax.vlines(mean_fem, 0, height_fem, color=purple, ls=':')

#mean_m = df_viz.groupby('race').age.median()[1]
#height_m = np.interp(mean_m, xs, ys)
#ax.vlines(mean_m, 0, height_m, color=green, ls=':')

#print(df_viz.groupby('race').age.median())

#plt.title('Distribution of Age by Race')
```
